\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Area of L-shapes and composite shapes — Excellence}}
\begin{tasks}(3)
\task {A composite shape consists of a 10 m × 6 m rectangle with a 4 m × 3 m rectangle removed from one corner and a right‑angled triangle of legs 5 m and 3 m added to the opposite side. Find the total area.}
\task {A garden is L‑shaped with outer dimensions 18 m by 12 m and cut‑out of 7 m by 5 m. Additionally, a circular pond of radius 2 m is removed from the remaining area. Find area of the garden (use \mbox{$\pi\approx 3.14$}).}
\task {A shape is formed by joining a rectangle 8 m × 5 m, a semicircle of diameter 5 m, and a right triangle of legs 4 m and 3 m. Calculate total area.}
\task {A room has an L‑shape with missing triangular corner; outer rectangle 16 m by 10 m, missing triangle base 8 m height 6 m. Additionally, a rectangular column 1 m by 1 m occupies the centre. Find floor area.}
\task {A pathway forms an L around a building; outer dimensions 25 m by 18 m, inner cut‑out rectangle 15 m by 10 m, and a 2 m wide walkway around the inner rectangle. Find area of the pathway (excluding the walkway overlap).}
\task {A composite shape consists of a 12 m × 8 m rectangle with a quarter‑circle of radius 4 m removed from one corner and a trapezium added to the opposite side (parallel sides 6 m and 4 m, height 3 m). Find area.}
\task {A garden is shaped as a rectangle 14 m by 9 m with a 5 m by 3 m rectangular flower bed removed from one corner, and a circular fountain of radius 1.5 m removed from the centre. Find remaining area.}
\task {A swimming pool has a composite shape: a 15 m × 10 m rectangle with a 6 m × 4 m rectangle cut out, and a semicircular shallow end of radius 5 m attached to the longer side. Find total water surface area.}
\task {Draw lines to split the shape into three rectangles, then calculate area given side lengths (some missing lengths must be deduced).}
\task {A shape consists of a 7 m × 5 m rectangle, a right triangle of legs 4 m and 3 m, and a quarter‑circle of radius 2 m. Calculate total area.}
\task {A room is L‑shaped with outer dimensions 20 m by 15 m, missing a 8 m by 6 m rectangle, and also missing a triangular corner of base 5 m and height 4 m. Find area of the room.}
\task {A pathway around a building forms an L; the outer rectangle is 30 m by 20 m, the inner rectangle is 18 m by 12 m, and the pathway width varies: 2 m on the longer side, 1.5 m on the shorter side. Calculate pathway area.}
\end{tasks}

\end{document}
