\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Area of L-shapes and composite shapes — Foundation}}
\begin{tasks}(3)
\task {Draw a dotted line to split the L‑shape into two rectangles.}
\task {Find the area of an L‑shape formed by a 6 m × 4 m rectangle joined to a 3 m × 2 m rectangle.}
\task {Calculate the area of a room shaped like an L: outer dimensions 10 m by 7 m, missing a 4 m by 3 m corner.}
\task {A garden has an L‑shape: 8 m long, 5 m wide, with a 3 m by 2 m cut‑out. Find the area.}
\task {Draw a dotted line to split the shape into two rectangles (different orientation).}
\task {Find the area of an L‑shape where the longer arm is 9 m × 3 m and the shorter arm is 2 m × 4 m.}
\task {Calculate the area of a pathway forming an L around a building: 12 m long, 6 m wide, with a 5 m by 4 m corner missing.}
\task {A swimming pool has an L‑shape: 15 m by 10 m, with a 6 m by 4 m cut‑out. Find its area.}
\task {Draw a dotted line to split the L‑shape into two rectangles (one vertical, one horizontal).}
\task {Find the area of an L‑shape formed by a 7 m × 5 m rectangle and a 4 m × 3 m rectangle.}
\task {Calculate the area of an L‑shaped patio: outer rectangle 11 m by 8 m, missing a 5 m by 3 m square.}
\task {A flower bed is L‑shaped: 9 m long, 6 m wide, with a 4 m by 2 m cut‑out. Find the area.}
\end{tasks}

\end{document}
