\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Foundation}}
\begin{tasks}(3)
\task List the two possible outcomes when a fair coin is tossed.
\task A fair die is rolled. Write the possible scores.
\task A spinner has red, blue, green, and yellow sectors. List the possible colours.
\task A bag contains only black and white counters. Name the possible colours you could pick.
\task Which is more likely on a fair coin: heads or tails?
\task Which is impossible on a standard die: rolling \mbox{$4$} or rolling \mbox{$8$}?
\task Which is certain on a standard die: rolling a number less than \mbox{$7$} or rolling a \mbox{$9$}?
\task Write the probability of getting heads on a fair coin as a fraction.
\task Write the probability of rolling a \mbox{$6$} on a fair die as a fraction.
\task Write the probability of rolling an even number on a fair die as a fraction.
\task A spinner has \mbox{$3$} equal sectors labelled \mbox{$A$}, \mbox{$B$}, and \mbox{$C$}. What is the probability of landing on \mbox{$B$}?
\task A bag has \mbox{$5$} counters: \mbox{$2$} red and \mbox{$3$} blue. What colour is more likely to be picked?
\task Is rolling a \mbox{$7$} on a standard die possible, impossible, or certain?
\task Is getting either heads or tails on one coin toss possible, impossible, or certain?
\task Which is more likely on a fair die: rolling an odd number or rolling a \mbox{$6$}?
\task Fill in the blank: the sample space for a fair coin is \mbox{$\{\square,\square\}$}.
\end{tasks}

\end{document}
