\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Proficient}}
\begin{tasks}(3)
\task Write the probability of rolling a factor of \mbox{$12$} on a fair die in F/T form.
\task Write the probability of rolling a multiple of \mbox{$2$} on a fair die in F/T form.
\task Write the probability of choosing a consonant from cards labelled \mbox{$A$}, \mbox{$E$}, \mbox{$I$}, \mbox{$O$}, \mbox{$U$}, \mbox{$M$}, \mbox{$N$}, \mbox{$P$}.
\task Write the probability of picking a prime number from a fair spinner labelled \mbox{$1,2,3,4,5,6$}.
\task A bag has \mbox{$5$} red, \mbox{$3$} blue, and \mbox{$4$} green counters. Write the probability of picking blue in F/T form.
\task A bag has \mbox{$2$} yellow, \mbox{$2$} black, and \mbox{$6$} white counters. Write the probability of not picking white in F/T form.
\task A standard deck card is chosen. Write the probability of drawing a heart in F/T form.
\task A standard deck card is chosen. Write the probability of drawing a face card in F/T form.
\task Two coins are tossed. Write the probability of getting exactly one head in F/T form.
\task Two coins are tossed. Write the probability of getting two tails in F/T form.
\task A fair die is rolled. Write the probability of getting a number greater than \mbox{$4$} in F/T form.
\task A fair die is rolled. Write the probability of not getting a multiple of \mbox{$3$} in F/T form.
\task Fill in the blank: if an event has \mbox{$3$} favourable outcomes out of \mbox{$8$} total outcomes, then \mbox{$P(\text{event})=\frac{\square}{\square}$}.
\task Fill in the blank: for a fair spinner with \mbox{$10$} equal sectors, if \mbox{$4$} sectors are shaded then \mbox{$P(\text{shaded})=\frac{\square}{10}$}.
\task Which is greater: the probability of drawing a black card from a standard deck or the probability of rolling an odd number on a fair die?
\task Which is smaller: the probability of exactly one head in two coin tosses or the probability of drawing a king from a standard deck?
\task A student says \mbox{$P(\text{prime on a fair die})=\frac{4}{6}$}. Are they correct?
\task Explain in one short sentence what the \mbox{$T$} stands for in F/T.
\end{tasks}

\end{document}
