\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Converting between length units — Excellence}}
\begin{tasks}(3)
\task A runner completes 2.5 km, 1800 m, and 750 m. Find the total distance in kilometres.
\task A map path is 12.4 cm long. If 1 cm represents 250 m, what is the real distance in kilometres?
\task A wire is 3.6 m long. It is cut into pieces of 45 mm each. How many full pieces can be made?
\task A truck travels 18 km, then 950 m, then 1.25 km. Give the total distance in metres.
\task A classroom is 8.4 m long and 620 cm wide. What is the difference between the length and width in cm?
\task A roll of tape contains 12 m of tape. If each use takes 18 cm, how many full uses are possible?
\task A hiker walks 4.75 km each day for 6 days. Give the total distance in metres.
\task A ribbon is 2.4 m long. One-third is cut off. Give the length removed in cm.
\task A road sign says the town is 7.5 km away. A cyclist has already travelled 3200 m. How much farther is it in metres?
\task Convert 0.0085 km to mm.
\task A pipe is 1500 mm long. A second pipe is 1.35 m long. Find their combined length in cm.
\task A race is 10 km long. Maia has completed 3650 m. What fraction of the race remains? Give the remaining distance in km as well.
\task A carpenter has 5 planks, each 1.8 m long. She uses 275 cm in total. How many centimetres remain?
\task Explain why converting from a smaller unit to a larger unit makes the number smaller, using one example.
\task A courier route is 0.85 km, 920 m, 1350 m, and 2.4 km. Find the total route length in km.
\end{tasks}

\end{document}
