\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task A student says the lowest common multiple of \mbox{$4$} and \mbox{$6$} is \mbox{$10$}. Are they correct? Explain.
\task A student says \mbox{$36$} is the lowest common multiple of \mbox{$6$} and \mbox{$9$}. Are they correct? Explain.
\task Write the first 3 common multiples of \mbox{$6$} and \mbox{$8$}.
\task Write the first 3 common multiples of \mbox{$9$} and \mbox{$12$}.
\task Find the lowest common multiple of \mbox{$8$} and \mbox{$14$}.
\task Find the lowest common multiple of \mbox{$12$} and \mbox{$15$}.
\task Find the lowest common multiple of \mbox{$18$} and \mbox{$24$}.
\task Fill in both blanks: the first two common multiples of \mbox{$4$} and \mbox{$9$} are \mbox{$\square$} and \mbox{$\square$}.
\task Fill in the blank: the lowest common multiple of \mbox{$a$} and \mbox{$6$} is \mbox{$18$} when \mbox{$a=\square$}.
\task Which does not belong: \mbox{$12, 18, 24, 30$} as common multiples of \mbox{$3$} and \mbox{$6$}?
\task Which is greater: the lowest common multiple of \mbox{$6$} and \mbox{$10$}, or the lowest common multiple of \mbox{$8$} and \mbox{$12$}? Show enough working to justify.
\task Three lights flash every \mbox{$6$}, \mbox{$8$}, and \mbox{$12$} seconds. After how many seconds will they all flash together again?
\task A bus comes every \mbox{$9$} minutes and a train comes every \mbox{$15$} minutes. If they leave now at the same time, after how many minutes will they leave together again?
\task Is \mbox{$48$} a common multiple of \mbox{$6$} and \mbox{$8$}? Is it the lowest common multiple? Explain.
\task Complete: if the lowest common multiple of \mbox{$5$} and \mbox{$n$} is \mbox{$35$}, then \mbox{$n=\rule{1.6cm}{0.15mm}$}.
\task Explain why the lowest common multiple of two numbers must be a multiple of both numbers.
\end{tasks}

\end{document}
