\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Excellence}}
\begin{tasks}(2)
\task A student says \mbox{$\sqrt{81}$} is irrational because it has a root sign. Correct? Explain.
\task A student says \mbox{$0.272727\ldots$} is irrational because it goes on forever. Correct? Explain.
\task A student says \mbox{$\pi=\frac{22}{7}$}. Correct? Explain.
\task Which is greater: \mbox{$\sqrt{18}$} or \mbox{$4.3$}? Show enough working.
\task Which is smaller: \mbox{$\sqrt{50}$} or \mbox{$7.1$}? Explain.
\task Put in ascending order: \mbox{$3,\ \sqrt{10},\ \pi,\ \sqrt{11}$}.
\task Put in descending order: \mbox{$\sqrt{5},\ 2.3,\ \frac{9}{4},\ \sqrt{6}$}.
\task \mbox{$\sqrt{30}$} lies between which consecutive integers?
\task \mbox{$\sqrt{70}$} lies between which consecutive integers?
\task Complete: an irrational number is \rule{2.2cm}{0.15mm} a terminating decimal.
\task Complete: \mbox{$\sqrt{\square}$} is rational when the number inside is a perfect square.
\task Which does not belong: \mbox{$\sqrt{9},\ \sqrt{16},\ \sqrt{18},\ \sqrt{25}$}?
\task Which does not belong: \mbox{$0.125,\ \frac{1}{8},\ \sqrt{2},\ 2.5$}?
\task Is \mbox{$2\pi$} rational or irrational? Give a short reason.
\task Is \mbox{$\sqrt{3}+1$} rational or irrational? Give a short reason.
\task A square has area \mbox{$12\text{ cm}^2$}. Its side length is \mbox{$\sqrt{12}$} cm. Between which two whole cm does it lie?
\task A circle has diameter \mbox{$1$} m. Is circumference \mbox{$\pi$} m rational or irrational?
\task Why is \mbox{$1.414$} rational even though it approximates an irrational number?
\end{tasks}

\end{document}
