\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=6.0em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}
\begin{document}
\sffamily
\boldmath

{\LARGE \textbf{Weight — Excellence}}
\begin{tasks}(3)
\task A truck carries 2.5 t of cargo. If each pallet weighs 375 kg, how many full pallets fit without exceeding the cargo mass?
\task A recipe uses 3.5 kg flour split equally into 7 containers. What mass does each container hold (in grams)?
\task A cargo limit is 12000 kg. A shipment has boxes: 8 x 950 kg, 5 x 1.2 t, and 12 x 45 kg. Is the shipment within the limit? Show calculations.
\task A cylindrical drum holds 200 L of oil; density = 0.88 kg/L. Find mass of oil in kg and t.
\task A boat displaces 0.75 t of water per cubic metre. If boat volume below waterline is 2.4 cubic metres, what is displaced mass in kg?
\task A machine part weighs 0.0035 t. Convert into kg and express as a fraction of 1 t.
\task An athlete lifts a total of 18.6 kg across 3 lifts, where two lifts are equal and the third is 2.4 kg heavier. Find the weights of each lift.
\task Explain why using tonnes may be better than kilograms for heavy machinery and provide one real-world example.
\end{tasks}

\end{document}
