\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task A student says \mbox{$41$} heads in \mbox{$80$} tosses proves a coin is unfair. Are they correct? Explain.
\task A spinner has four equal sectors, so the theoretical probability of red is \mbox{$\frac{1}{4}$}. In \mbox{$12$} spins red appears \mbox{$6$} times. Compare the experimental and theoretical probabilities.
\task A bar chart shows bus arrivals over \mbox{$50$} days: early \mbox{$8$}, on time \mbox{$29$}, late \mbox{$13$}. Estimate the probability that tomorrow\'s bus is late.
\task A survey of \mbox{$120$} students shows \mbox{$54$} bring lunch, \mbox{$42$} buy lunch, and \mbox{$24$} go home. Estimate the probability a randomly chosen student buys lunch.
\task A basketball player scores \mbox{$63$} shots from \mbox{$90$} attempts. Estimate the probability of scoring, as a fraction in simplest form and as a percentage.
\task In a science test, \mbox{$18$} of \mbox{$30$} seedlings survive in one tray and \mbox{$52$} of \mbox{$80$} survive in another. Which tray has the higher survival probability?
\task A machine makes faulty items with theoretical probability \mbox{$0.08$}. In a sample of \mbox{$150$} items, \mbox{$18$} are faulty. Is the experimental probability above or below the theoretical probability?
\task A coin is tossed \mbox{$200$} times and lands heads \mbox{$94$} times. Is this result closer to \mbox{$0.45$}, \mbox{$0.47$}, or \mbox{$0.50$}? Explain.
\task Which is greater: \mbox{$17$} wins from \mbox{$40$} games or \mbox{$31$} wins from \mbox{$70$} games? Show enough working to justify.
\task A hospital record shows \mbox{$126$} of \mbox{$300$} patients waited under \mbox{$15$} minutes. Estimate the probability that the next patient waits under \mbox{$15$} minutes.
\end{tasks}

\end{document}
